---
title: "Simulation Outputs"
output: html_notebook
---

# Setup

```{r Load libraries and functions}
# Libraries --------------
library(dplyr); library(ggplot2); library(ggpubr);library(Pabloverse); library(sf)
library(rpart); library(randomForest); library(caret)
 
# FUNCTIONS --------------
# Function to read the sims -------
ReadSims <- function(d) {
  f <- list.files(d, full.names = T)
  D <- lapply(f, function(x) {
    read.csv(x)
  }) %>%
    do.call(rbind, .)
  return(D)
}
# Function to read the directories --------------
ReadDirs <- function(d){
  dirs <- list.dirs(d, recursive = F)
  Ld <- lapply(dirs, ReadSims)
  names(Ld) <- gsub(d, '', dirs) %>%  gsub('([^A-z])', '', .)
  return(Ld)
}
# Function for summary tables ---------------
SumTbl <- function(d){
  d %>% 
    summarise_at(.vars = c('AtkRate', 'Cumulative_I', 'Cumulative_I_r', 'Cumulative_I_s', 'Cumulative_H', 'D', 'LastInfection'),
                 .funs = c('mean' =  ~round(wilcox.test(., conf.int = T)$estimate, 2),
                           'q05' = ~round(wilcox.test(., conf.int = T)$conf.int[1], 2),
                           'q95' = ~round(wilcox.test(., conf.int = T)$conf.int[2], 2))) %>% 
    data.frame() %>% 
  mutate(LastInfection = paste0(LastInfection_mean, ' (', LastInfection_q05, ', ', LastInfection_q95, ')'),
         AtkRate = paste0(AtkRate_mean, ' (', AtkRate_q05, ', ', AtkRate_q95, ')'),
         Cumulative_I = paste0(Cumulative_I_mean, ' (', Cumulative_I_q05, ', ', Cumulative_I_q95, ')'),
         Cumulative_I_r = paste0(Cumulative_I_r_mean, ' (', Cumulative_I_r_q05, ', ', Cumulative_I_r_q95, ')'),
         Cumulative_I_s = paste0(Cumulative_I_s_mean, ' (', Cumulative_I_s_q05, ', ', Cumulative_I_s_q95, ')'),
         Cumulative_H = paste0(Cumulative_H_mean, ' (', Cumulative_H_q05, ', ', Cumulative_H_q95, ')'),
         D = paste0(D_mean, ' (', D_q05, ', ', D_q95, ')')
         )
}

Tbl <- function(d, x){
  d %>% 
    group_by(seed) %>%
    slice(n()) %>%
    group_by({{x}}) %>%
    SumTbl() %>%
    select({{x}}, LastInfection:D) 
}
# Function to get the plots -------------------
RFCART <- function(data, f, main = '', seed = 1, palette  ='-RdYlGn'){
  PL <- list()
  
  set.seed(seed)
  # Split the data train/test
  ind <- sample(2, nrow(data), replace = TRUE, prob = c(0.7, 0.3))
  train <- data[ind==1,]
  test <- data[ind==2,]
  # Random Forest model fit
  rf <- randomForest::randomForest(f, data=train, proximity=TRUE) 
  print(rf)
  
  # Variable importance
  PL[[2]] <- importance(rf) %>%
    data.frame() %>% 
    mutate(variable = rownames(.), RelImpt = IncNodePurity/sum(IncNodePurity)) %>%
    ggplot(aes(x = reorder(variable, RelImpt), y = RelImpt)) +
    geom_col() +
    coord_flip() +
    labs(x = '', y = 'Relative Importance', title = main) +
    theme_minimal() +
    theme(axis.text=element_text(size=14),
        axis.title=element_text(size=16,face="bold"))
  
  # tr <- tree::tree(f, data=data)
  # plot(tr); text(tr)
  fit <- rpart(f, data=data, method = 'anova')
  PL[[1]] <- rpart.plot::rpart.plot(fit, type = 4, box.palette = palette, branch.lty = 2)
  
  return(PL)
}
ICurveP <- function(x){
  d$EC %>% 
    mutate(day = floor(cycle/24)) %>%
    # group_by(seed) %>% 
    # mutate(L = n()) %>% ungroup() %>% mutate(mL = max(L), dL = mL - L) %>%  group_by(seed) %>% slice(c(1:n(),rep(n(), max(dL)))) %>% 
    # ungroup() %>% arrange(seed, day) %>% 
    group_by(day, {{x}}) %>% 
    summarise(MeanCI = mean(Cumulative_I), MedianCI = median(I)) %>% 
   ggplot() +
  geom_line(aes(day, MeanCI, col = factor({{x}})), lwd = 0.5) +
  Pabloverse::Theme1()
}

BoxPlot <- function(d, x, y, ColPal = 1:5) {
  d %>%
    group_by(seed, {{y}}) %>%
    filter(cycle == max(cycle)) %>%
    ggplot() +
    geom_boxplot(aes({{x}}, fill = {{y}}), alpha = 0.8, col = 'black') +
    coord_flip() +
    scale_fill_manual(values = ColPal)
}

# Function for linear regression estimates ---------------------------
LmCI <- function(d, f, a = 0.05) {
  # fit the model
  m <- d %>%
    lm(f, data = .)
  # obtain coefficients and CI
  coef <- round(m$coefficients, 2) # coefficients
  ci <- round(confint(m), 2) # CI
  p <- broom::glance(m)$p.value
  sig <- ifelse(p < a, '$^*$', '')
  # Paste it in a string
  est <- paste0(coef, '(', ci[,1], ',', ci[,2], ')', sig)
  names(est) <- names(coef)
  # data.frame(Var = names(coef), est) %>% 
    return(est)
}
```

## Load the simulations

```{r load the data}
N <- 170 + 174 # Total population
p <- "../GAMA_NHCOVID/NH_COVID/models/results/GSA/" # Directory for simulations
d <- ReadDirs(p) # Read all the simulations
Outcomes <- c('I', 'Cumulative_I', 'I_r', 'I_s', 'Introductions', 'PassiveDet_s', 'ActiveDet_s', 'PassiveDet_r', 'ActiveDet_r') # Outcomes analyzed
Var <- c('GlobalShedding_p', 'AsymptTransmission', 'Introduction_p', 'TestingFreq', 'detection_p', 'SR_OR', 'PPE_OR',  'vaccination_dist', 'VaccineEff') # Model parameters examined


d$EC <- d$EC %>% 
  mutate(Cumulative_I = Cumulative_I_r + Cumulative_I_s, # Total infected (Staff + residents)
         AtkRate = Cumulative_I / N, # Attack rate
         LastInfection = (LastInfection/24) + 0, # Add days of sickness (in average, fix this later in the model)
         detection_p = Test_sensitivity) %>% 
  mutate_at(Var, factor) %>% # Convert all model parameters examined to factor
  mutate(Introduction_p = recode(as.character(Introduction_p), `0.01` = 'Low', `0.05` = 'Medium', `0.1` = 'High')) %>% 
  data.frame()

# Get the cumulative numbers for each simulation run
d$Cum <- d$EC %>% 
  group_by(seed) %>% 
  slice(n()) %>% 
  data.frame()

d$ECo <- d$EC %>% 
  group_by(seed) %>% 
  mutate(T_I_r = max(Cumulative_I_r)) %>% 
  data.frame() %>% 
  filter(T_I_r > 1)


# How long did it took to run? (in minutes, must be from continuous runs)
d$EC %>% 
  group_by(seed) %>% 
  summarise(t = (max(t) - min(t))/(1000*60)) %>% 
  pull(t) %>% 
  mean()
# Total simulations
nrow(d$Cum)
```

### Corplot 

```{r}
ds <- d$Cum %>% 
  select(c(Outcomes, Var)) %>%
  mutate_all(~as.numeric(as.factor(.)))
  
  # count(seed, .dots=lapply(c(Outcomes, Var), as.symbol)) %>% 
  # select(-seed, -n) %>% 
  # mutate_all(~as.numeric(as.factor(.)))
ds %>% 
  # count(TestingFreq, PPE_OR)
  # count(TestingFreq, Introduction_p)
  count(detection_p, PPE_OR)
  # count(AsymptTransmission, Introduction_p)

corrplot::corrplot(cor(ds))
```

# Validation

The model was calibrated and validated with data on confirmed COVID-19 cases reported between May 24, 2020, and February 14, 2021, in California nursing homes with similar resident census (between 150 and 200 occupied beds) extracted from the Centers for Medicare & Medicaid Services (CMS)

```{r Prepare the data}
# Load and filter the CMS data
CMS_CA <- read.csv("../../Data/CMS/COVID-19_Nursing_Home_Dataset.csv") %>%
  mutate(date = as.Date(Week.Ending, format = '%m/%d/%Y')) %>% # format the date
  filter(Provider.State == "CA") # Filter to CA only

# Data from interviewed NH
CVS <- CMS_CA %>%
  filter(Provider.Name == 'CLEAR VIEW SANITARIUM') %>%
  arrange(date) %>%
  filter(Residents.Total.Confirmed.COVID.19 > 0) %>% # filter only where > 1 infected
  mutate(I = Residents.Total.Confirmed.COVID.19 + Staff.Total.Confirmed.COVID.19) %>% # Get total infected
  select(Provider = Federal.Provider.Number, I, date, Ir_cumsum = Residents.Total.Confirmed.COVID.19, IS_cumsum = Staff.Total.Confirmed.COVID.19) %>% 
  mutate(day = (date - first(date)) + 7)
```


```{r Observed data}
range(CMS_CA$date) # Range of dates

# Format the data:
CMSCA_ts <- CMS_CA %>% 
  replace(is.na(.), 0) %>% # replace NAs with 0
  # Select only relevant variables
  select(date, Provider = Federal.Provider.Number, Ir = Residents.Weekly.Confirmed.COVID.19, Is = Staff.Weekly.Confirmed.COVID.19, Dr = Residents.Weekly.COVID.19.Deaths, OccBeds = Total.Number.of.Occupied.Beds) %>%
  arrange(Provider, date) %>% # Sort by date and provider
  group_by(Provider) %>% #group by provider
  mutate_at(.vars = c('Ir', 'Is', 'Dr'), .funs = c('cumsum', 'sum')) %>% # Get cumulative numbers
  mutate(CumI = Ir_cumsum + Is_cumsum,
         TotalI = Ir_sum + Is_sum) %>%
  filter(CumI > 0) %>%
  mutate(OccBeds = max(OccBeds), 
         d = date - first(date), 
         p_infection = Ir_sum/OccBeds, 
         I = Ir + Is) %>%
  filter(between(OccBeds, 160, 200),
         TotalI != CumI)

Obs <- CMSCA_ts %>% data.frame() %>%
  filter(d < 150) %>%
  mutate(day = d, type = "observed") %>%
  select(day, CumI, type, Ir_cumsum, Is_cumsum, Sim = Provider)



Obs_s <- Obs %>% 
  group_by(day, type) %>% 
  summarise_at(.vars = c('CumI', 'Ir_cumsum', 'Is_cumsum'), 
               .funs = c(m = ~quantile(., 0.5), q05 = ~quantile(., 0.25), q95 = ~quantile(., 0.75)))%>% 
  mutate(day = as.numeric(day))
```

## Observed vs sim

```{r}
B <- d$EC %>% 
  filter(TestingFreq == 7) %>%
  filter(Introduction_p == "Medium") %>%
  filter(vaccination_dist == 0) %>%
  # filter(detection_p == 0.8) %>%
  filter(PPE_OR == 0.1467) %>%
  filter(GlobalShedding_p %in% c(0.38, 0.38*1.2)) %>%
  # filter(TestingFreq == 7, vaccination_dist == 0, GlobalShedding_p == 0.35) %>%
  data.frame()

Exp <- B %>%
  mutate(day = cycle/24, CumI = Cumulative_I_r + Cumulative_I_s, type = "simulated") %>% 
  # Repeat the last row 150 times
  group_by(seed) %>%
  mutate(tMinus = 150 - max(day)) %>%
  slice(c(1:n(), rep(n(), 150))) %>%
  mutate(day = 1:n()) %>%  # Change the day number in order
  slice(1:150) %>% # select the first 150 of each group (seed)
  select(day,LastInfection,  CumI, type, Ir_cumsum = Cumulative_I_r, Is_cumsum = Cumulative_I_s, Sim = seed, Introductions) %>% 
  group_by(day, type) 

Exp_s <- Exp %>% 
  summarise_at(.vars = c('LastInfection', 'CumI', 'Ir_cumsum', 'Is_cumsum', 'Introductions'), 
               .funs = c(m = ~quantile(., 0.5), q05 = ~quantile(., 0.05), q95 = ~quantile(., 0.95))
               )

Ob_Ex <- rbind(Obs_s, Exp_s)
OEp <- list()

B %>%
  group_by(seed) %>% 
  slice(n())

B %>% mutate(i = 1) %>% Tbl(., i)

OEp[[1]] <- Ob_Ex %>% 
  ggplot(aes(x = day)) +
  geom_ribbon(aes(ymin = Is_cumsum_q05, ymax = Is_cumsum_q95, fill = type, col = type), alpha = 0.15) +
  geom_line(aes(y = Is_cumsum_m, col = type), lwd = 1, alpha = 0.8) +
  geom_point(data = CVS, aes(y = IS_cumsum, alpha = ''), shape = 18, size = 2.5, col = 'black') +
  scale_color_manual(values = c('red3', "blue3")) +
  scale_fill_manual(values = c('red2', "blue2")) +
  theme_minimal() +
  scale_alpha_manual(values = 1) +
  labs(title = 'Staff', y = 'Median', x = 'Day', alpha = 'LCF Interviewed') +
  xlim(c(0, 150))

OEp[[2]] <- Ob_Ex %>% 
  ggplot(aes(x = day)) +
  geom_ribbon(aes(ymin = Ir_cumsum_q05, ymax = Ir_cumsum_q95, fill = type, col = type), alpha = 0.15) +
  geom_line(aes(y = Ir_cumsum_m, col = type), lwd = 1, alpha = 0.8) +
  geom_point(data = CVS, aes(y = Ir_cumsum, alpha = ''), shape = 18, size = 2.5, col = 'black') +
  scale_color_manual(values = c('red3', "blue3")) +
  scale_fill_manual(values = c('red2', "blue2")) +
  theme_minimal() +
  scale_alpha_manual(values = 1) +
  labs(title = 'Residents', y = 'Median', x = 'Day', alpha = 'LCF Interviewed') +
  xlim(c(0, 150))

ggarrange(plotlist = OEp, common.legend = T) %>% 
  annotate_figure(top = "Observed vs simulated outbreaks") 
# %>% 
  # ggsave(filename = '../../Documentation/Figures/V2/ObsExp.png', width = 8, height = 4.5)
```

### Validation

```{r}
# Correlation and R^2
dm <- rbind(Obs, Exp[-c(2, 8)]) %>%
  group_by(day, type) %>%
  summarise_at(.vars = c('CumI', 'Ir_cumsum', 'Is_cumsum'), .funs = median) %>%
  arrange(type) %>%
  data.frame()

odays <- dm %>%
  filter(type == 'observed') %>%
  pull(day)

dms <- dm %>%
  filter(day %in% odays, 
         day != 0) %>%
  split(.$type)

#Correlation
pIt <- cor(dms$observed$CumI, dms$simulated$CumI)
pIr <- cor(dms$observed$Ir_cumsum, dms$simulated$Ir_cumsum)
pIs <- cor(dms$observed$Is_cumsum, dms$simulated$Is_cumsum)

R2t <- lm(dms$observed$CumI~dms$simulated$CumI) %>%
  summary() %>%
  .$r.squared

R2r <- lm(dms$observed$Ir_cumsum~dms$simulated$Ir_cumsum) %>%
  summary() %>%
  .$r.squared

R2s <- lm(dms$observed$Is_cumsum~dms$simulated$Is_cumsum) %>%
  summary() %>%
  .$r.squared
```

## Overview (univariate)

```{r overall outbreak size}
d$EC %>% 
  group_by(seed) %>% 
  filter(cycle == max(cycle)) %>% 
  ggplot() +
  geom_histogram(aes(AtkRate))

nvd <- d$EC %>% filter(vaccination_dist == 0.0, PPE_OR == 0.1467)

BoxPlot(d = d$EC, x = AtkRate, y = GlobalShedding_p)
Tbl(d = d$EC, x = GlobalShedding_p)
BoxPlot(d = d$EC, x = AtkRate, y = Introduction_p)
Tbl(d = d$EC, x = Introduction_p)
BoxPlot(d = d$EC, x = AtkRate, y = detection_p)
Tbl(d = d$EC, x = detection_p)
BoxPlot(d = d$EC, x = AtkRate, y = PPE_OR)
Tbl(d = d$EC, x = PPE_OR)
BoxPlot(d = d$EC, x = AtkRate, y = AsymptTransmission)
Tbl(d = d$EC, x = AsymptTransmission)
BoxPlot(d = d$EC, x = AtkRate, y = vaccination_dist)
Tbl(d = d$EC, x = vaccination_dist)
BoxPlot(d = nvd, x = AtkRate, y = TestingFreq)
Tbl(d = nvd, x = TestingFreq)
BoxPlot(d = d$EC, x = AtkRate, y = SR_OR)
Tbl(d = d$EC, x = SR_OR)

BoxPlot(d = d$EC %>% filter(vaccination_dist != 0), x = AtkRate, y = VaccineEff)
Tbl(d = d$EC, x = VaccineEff)
```

### ~Experimental function~

```{r}
f <- 'LastInfection~GlobalShedding_p'

Outcomes <- c('LastInfection', 'AtkRate', 'Cumulative_I', 'Cumulative_I_r', 'Cumulative_I_s', 'Cumulative_H', 'D')

Vs <- c('GlobalShedding_p', 'Introduction_p', 'detection_p', 'PPE_OR', 'AsymptTransmission', 'SR_OR')
# , 'vaccination_dist', , )
Ut <- list()
Ut[[1]] <- lapply(Vs, function(y){
  lapply(Outcomes, function(x){
  LmCI(d = d$Cum %>% 
         mutate_at(Vs, .funs = ~relevel(factor(.), 2)) %>% 
         mutate(Introduction_p = relevel(Introduction_p, 'Medium'),
                TestingFreq = relevel(TestingFreq, '7'),
                SR_OR = relevel(SR_OR, '1')) %>% 
         filter(., vaccination_dist == 0), f = paste0(x, '~', y))
}) %>% 
  do.call(cbind, .) %>% 
  data.frame() %>% `names<-`(Outcomes)
}) %>% 
  do.call(rbind, .) 

Ut[[2]] <- lapply(Outcomes, function(x){
  LmCI(d = d$Cum  %>%
         mutate(TestingFreq = relevel(TestingFreq, '7')) %>%
         filter(PPE_OR == 0.1467) %>%
         filter(., vaccination_dist == 0),
       f = paste0(x, '~', 'TestingFreq'))
}) %>% 
  do.call(cbind, .) %>% 
  data.frame() %>% `names<-`(Outcomes)

# Vaccine distribution
Ut[[3]] <- lapply(Outcomes, function(x){
  LmCI(d = d$Cum  %>%
         mutate(vaccination_dist = relevel(vaccination_dist, '0'))
       , f = paste0(x, '~', 'vaccination_dist'))
}) %>% 
  do.call(cbind, .) %>% 
  data.frame() %>% `names<-`(Outcomes)
# Vaccine efficacy
Ut[[4]] <- lapply(Outcomes, function(x){
  LmCI(d = d$Cum  %>%
         filter(vaccination_dist != 0) %>% 
         mutate(VaccineEff = relevel(VaccineEff, 'Equal'))
       , f = paste0(x, '~', 'VaccineEff'))
}) %>% 
  do.call(cbind, .) %>% 
  data.frame() %>% `names<-`(Outcomes)

Ut %>% 
  do.call(rbind, .) %>% 
  write.csv('../../Documentation/Tables/Univ.csv', quote = F, sep = '&')
```

```{r}
d$Cum %>% 
  filter(GlobalShedding_p == 0.304) %>% 
  group_by(i = 1) %>% 
  summarise_at(Outcomes, .funs = ~mean(.))
```

## Bivar

```{r bivariate boxplot, fig.height=7, fig.width=7}
BoxPlot.Bi <- function(d, x, y, z, ColPal = c(1, 2, 3)) {
  d %>%
    group_by(seed, {{y}}, {{z}}) %>%
    filter(cycle == max(cycle)) %>%
    ggplot() +
    geom_boxplot(aes({{x}}, fill = {{y}}), alpha = 0.6) +
    facet_wrap(vars({{z}}))+
    coord_flip() +
     scale_fill_manual(values = ColPal) +
    theme_minimal() +
    theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        strip.background = element_rect(colour="black",
                                        fill="grey90")) +
    theme(legend.position = 'top')
}
dc <- d$EC %>% 
  # filter(Introduction_p == 0.01) %>%
  # filter(vaccination_dist == 0) %>%
  # filter(GlobalShedding_p %in% c(0.25)) %>%
  # filter(vaccination_dist != 0) %>%
  group_by(seed) %>% 
  slice(n())%>% 
  mutate(Cumulative_I = Cumulative_I_r + Cumulative_I_s, D = D*4)

PSc <- list()

PSc[[1]] <- d$Cum %>% 
  mutate(Introduction_p = factor(Introduction_p, levels = c('Low', 'Medium', 'High'))) %>%
  filter(vaccination_dist == 0) %>% 
  # mutate(TestingFreq = relevel(TestingFreq, ref = '7')) %>% 
  filter(PPE_OR == c(0.1467)) %>%
  # filter(PPE_OR %in% c(0.1467),  detection_p %in% c(1.2*0.8)) %>%
  BoxPlot.Bi(d = ., x = AtkRate, y = TestingFreq, z = Introduction_p, ColPal =  c("#C70704", "#BAB700", "#008C0C"))

PSc[[2]] <- filter(d$EC, PPE_OR == 0.1467) %>%
  mutate(Introduction_p = factor(Introduction_p, levels = c('Low', 'Medium', 'High'))) %>%
  filter(vaccination_dist != 0) %>% 
  mutate(`Vaccination Distribution` = recode(vaccination_dist, `0.3` = 'Resident Priority', `0.5` = 'Equal', `0.7` = 'Staff priority')) %>% 
  BoxPlot.Bi(d = ., x = AtkRate, y = `Vaccination Distribution`, z = Introduction_p, ColPal <- c("#414042", "#8C8700", "#5D0DB3"))

# PSc[[3]] <- filter(d$EC, PPE_OR == 0.1467) %>%
#   filter(vaccination_dist != 0) %>% 
#   mutate(`Vaccine Efficacy` = recode(VaccineEff, `A` = 'Pfizer', `B` = 'Moderna' )) %>% 
#   BoxPlot.Bi(d = ., x = AtkRate, y = `Vaccine Efficacy`, z = Introduction_p, ColPal <- c("#5C9669", "#6A918C", "#7280B3"))

ggarrange(plotlist = PSc, ncol = 1) %>%
  ggsave(filename = '../../Documentation/Figures/V2/Scenarios.png', width = 7, height = 7)
```


```{r}
d$Cum %>% 
  mutate(Introduction_p = factor(Introduction_p, levels = c('Low', 'Medium', 'High'))) %>%
  filter(vaccination_dist == 0) %>% 
  # mutate(TestingFreq = relevel(TestingFreq, ref = '7')) %>% 
  # filter(PPE_OR == c(0.1467)) %>%
  # filter(PPE_OR %in% c(0.1467),  detection_p %in% c(1.2*0.8)) %>%
  BoxPlot.Bi(d = ., x = AtkRate, y = TestingFreq, z = GlobalShedding_p, ColPal =  c("#C70704", "#BAB700", "#008C0C"))

d$Cum %>% 
  mutate(Introduction_p = factor(Introduction_p, levels = c('Low', 'Medium', 'High'))) %>%
  filter(vaccination_dist != 0) %>%
  # mutate(TestingFreq = relevel(TestingFreq, ref = '7')) %>% 
  # filter(PPE_OR == c(0.1467)) %>%
  # filter(PPE_OR %in% c(0.1467),  detection_p %in% c(1.2*0.8)) %>%
  BoxPlot.Bi(d = ., x = AtkRate, y = vaccination_dist, z = GlobalShedding_p, ColPal =  c("#C70704", "#BAB700", "#008C0C"))
```



```{r}
BTbl <- list()

BTbl[[1]] <- lapply(unique(d$Cum$Introduction_p), function(y){
  lapply(Outcomes, function(x){
  LmCI(d = d$Cum  %>%
         mutate(TestingFreq = relevel(TestingFreq, ref = '7')) %>% 
         filter(vaccination_dist == 0) %>% 
         filter(PPE_OR == c(0.1467)) %>%
         filter(Introduction_p == y),
       f = paste0(x, '~', 'TestingFreq'))
}) %>% 
  do.call(cbind, .) %>% 
  data.frame() %>%
    `names<-`(Outcomes) %>% 
  mutate(Var = rownames(.)) %>% 
    mutate(y = y)
}) %>% 
  do.call(rbind,.)

BTbl[[2]] <- lapply(unique(d$Cum$Introduction_p), function(y){
  lapply(Outcomes, function(x){
  LmCI(d = d$Cum  %>%
         filter(vaccination_dist != 0) %>% 
         mutate(vaccination_dist = relevel(vaccination_dist, ref = '0.5')) %>% 
         filter(Introduction_p == y),
       f = paste0(x, '~', 'vaccination_dist'))
}) %>% 
  do.call(cbind, .) %>% 
  data.frame() %>%
    `names<-`(Outcomes) %>% 
  mutate(Var = rownames(.)) %>% 
    mutate(y = y)
}) %>% 
  do.call(rbind,.)

BTbl %>% 
  do.call(rbind, .) %>% 
  write.csv('../../Documentation/Tables/Biv.csv', quote = F, row.names = F)
```


```{r}
LmSum <- function(f, d){
   m <- lm(f, d)
   coef <- round(m$coefficients, 4)
   ci <- round(confint(m), 4)

   data.frame(coef, ci) %>% 
     slice(-1) %>% 
     mutate(var = row.names(.), Est = paste0(coef, ' (', ci[1,], ',',ci[2,], ')')) %>% 
     select(var, Est) %>% 
     return()
}
```

```{r}
# Testing Frequency --------------
dc %>% 
  mutate(TestingFreq = relevel(TestingFreq, ref = '7')) %>% 
  # filter(detection_p %in% c(1.2*0.8))
  filter(PPE_OR %in% c(0.1467)) %>% 
  filter(vaccination_dist == 0.0) %>% 
  filter(Introduction_p == 'Low') %>%
  LmSum('AtkRate~TestingFreq', d = .)

dc %>% 
  mutate(TestingFreq = relevel(TestingFreq, ref = '7')) %>% 
  # filter(detection_p %in% c(1.2*0.8)) %>% 
  filter(PPE_OR %in% c(0.1467)) %>% 
  filter(vaccination_dist == 0.0) %>% 
  filter(Introduction_p == 'Medium') %>%
  LmSum('AtkRate~TestingFreq', d = .)

dc %>% 
  mutate(TestingFreq = relevel(TestingFreq, ref = '7')) %>% 
  # filter(detection_p %in% c(1.2*0.8)) %>% 
  filter(PPE_OR %in% c(0.1467)) %>% 
  filter(vaccination_dist == 0.0) %>% 
  filter(Introduction_p == 'High') %>%
  # lm(Cumulative_I~TestingFreq, .) %>% 
  # summary()
  LmSum('AtkRate~TestingFreq', d = .)
```

## GSA

```{r}
dc <- d$Cum %>% 
  # filter(Introduction_p == 0.01) %>%
  # filter(vaccination_dist == 0) %>%
  # filter(GlobalShedding_p %in% c(0.25)) %>%
  # filter(vaccination_dist != 0) %>%
 mutate_at(.vars = c('GlobalShedding_p', 'detection_p', 'AsymptTransmission', 'SR_OR'), .funs = ~factor(., labels = c('Low', 'Med', 'High')))%>% 
  mutate(PPE_OR = factor(PPE_OR, labels = c('High', 'Med', 'Low'))) %>% 
  mutate(vaccination_dist = recode(vaccination_dist, `0` = 'No vaccinaiton', `0.3` = 'Resident', `0.5` = 'Equal', `0.7` = 'Staff')) %>% 
  mutate(Cumulative_I = Cumulative_I_r + Cumulative_I_s)

####### Function to get the plots ##########
RFCART <- function(data, f, main = '', seed = 1, palette  ='-RdYlGn'){
  PL <- list()
  
  set.seed(seed)
  # Split the data train/test
  ind <- sample(2, nrow(data), replace = TRUE, prob = c(0.7, 0.3))
  train <- data[ind==1,]
  test <- data[ind==2,]
  # Random Forest model fit
  rf <- randomForest::randomForest(f, data=train, proximity=TRUE) 
  print(rf)
  
  # Variable importance
  PL[[2]] <- importance(rf) %>%
    data.frame() %>% 
    mutate(variable = rownames(.), RelImpt = IncNodePurity/sum(IncNodePurity)) %>%
    ggplot(aes(x = reorder(variable, RelImpt), y = RelImpt)) +
    geom_col() +
    coord_flip() +
    labs(x = 'Parameters', y = 'Relative Importance', title = main) +
    theme_minimal()
  
  # tr <- tree::tree(f, data=data)
  # plot(tr); text(tr)
  fit <- rpart(f, data=data, method = 'anova')
  PL[[1]] <- rpart.plot::rpart.plot(fit, type = 4, box.palette = palette, branch.lty = 2)
  
  return(PL)
}

dc <- dc %>% 
  mutate(Infection_p = GlobalShedding_p, `Asymptomatic transmission` = AsymptTransmission)

# Cummulative Infected
f1 <- Cumulative_I ~ Infection_p + AsymptTransmission + Introduction_p + TestingFreq + detection_p + PPE_OR + vaccination_dist + VaccineEff

RFCART(data = dc, f = f1)

# Cummulative Hosp
f2 <- Cumulative_H ~ Infection_p + AsymptTransmission + Introduction_p + TestingFreq + detection_p + PPE_OR + vaccination_dist + VaccineEff

RFCART(data = dc, f = f2)

# Cummulative Deaths
f3 <- D ~ Infection_p + AsymptTransmission + Introduction_p + TestingFreq + detection_p + PPE_OR + vaccination_dist + VaccineEff
RFCART(data = dc, f = f3)
```



```{r}
## Export the results
png(filename = '../../Documentation/Figures/V2/CumRTI.png', width = 6.5, height = 5,res = 300, units = 'in')
Ps <- RFCART(f = f1 ,data = dc, 
             main = '')
dev.off()
Ps[[2]]  %>%
  ggsave(filename = '../../Documentation/Figures/V2/CumI-VI.png', plot = ., width = 6.5, height = 2)

## Export the results
png(filename = '../../Documentation/Figures/V2/DRT.png', width = 6.5, height = 5,res = 300, units = 'in')
Ps <- RFCART(f = f3 ,data = dc, 
             main = '')
dev.off()
Ps[[2]]  %>%
  ggsave(filename = '../../Documentation/Figures/V2/D-VI.png', plot = ., width = 6.5, height = 2)
```


```{r CART Interactive version}
library(visNetwork)
r <- rpart(formula = f1, data = dc)

visTree(r, 
        colorEdges = '#6E0E0CC9', # color of the edges
        shapeY = 'diamond', # shpe of the outcome
        colorY = c("#F2D600", "#EB0400")) # color gradient c(min, max)
```

